Empirical Study of Scientific Computer Software: Objectives and Research Questions

### 2020-06-16 OverallResearchProposal/ObjectivesAndResearchQuestions.tex
Updates to objectives section, more explicitly splitting softifacts (knowledge) from process

\subsection* {Overall Objective}

@@

The overall objectives asks what is needed for produce softifacts sustainably.
We consider the \emph{what} to be the principles, processes and methodologies
used for software development.  We exclude tools from this list because,
although tools are needed to support processes and methodologies, tools change
rapidly.  Our goal is to be general.  If the right principles, processes and
methodologies are found, the tools will adapt to match.  However, understanding
the current state of the practice will involve looking at tools, as shown in the
later list of research questions (Section~\ref{Sec_ResearchQuestions}).  As
mentioned above, for sustainability to be achieved, the productivity of the
adopted process must be considered.

what else do we need - knowledge - knowledge captured in softifacts.  - overlap
plus duplication - required and desired, but still want to be productive.  To be
productive, want to say once and view as needed.  Suggests generation - maybe
put this elsewhere?

@@

Further information on the relevant definitions and context is given in the next
section.  Roadmap.

\subsection*{Context, Definitions and Assumptions} \label{Sec_Context}

@@

\subsubsection*{Definitions}

@@

\subsubsection*{Assumptions}

@@

\subsubsection*{Current State of the Practice Research Questions} \label{Sec_ResearchQuestions}

@@

\subsubsection*{Ideal Process}

>>>>

\section {Overall Objective}

@@

The overall objectives asks what is needed for produce softifacts sustainably.
The \emph{what} is found by answering two questions:

\begin{enumerate}
\item What softifacts, in addition to the code, are needed?
\item What software engineering principles, processes and methodologies should
  be employed?
\end{enumerate}

To determine what softifacts are necessary for sustainability, we need to
determine what knowledge needs to be captured and documented.  The knowledge
comes from the problem domain, from computing, from documentation rules and from
the development process.  We also need to determine how to document the
softifacts.  That is, what information should appear in which artifacts?, how
should it be formatted and structured?

The adopted software engineering principles, processes and methodologies
significantly contribute to sustainability.  We exclude tools from this list
because, although tools are needed to support processes and methodologies, tools
change rapidly.  Our goal is to be general.  If the right principles, processes
and methodologies are found, the tools will adapt to match.  However,
understanding the current state of the practice will involve looking at tools,
as shown in the later list of research questions
(Section~\ref{Sec_ResearchQuestions}).  For sustainability to be achieved, the
productivity of the adopted process must be considered.  The process should lead
to high quality artifacts with, as mentioned earlier, a reasonable amount of
effort.

To be successful, the process, methods and tools, need:

to avoid repetition (knowledge should only be entered once)
reduce/remove drudgery
provide flexibility for change
I think there are more things in this list ...

This leads to our hypothesis: We can use a process that uses knowledge capture
and artifact generation to avoid repetition, reduce drudgery and provide
flexibility.  We have been calling this process MDE, although I'm not sure
@carette is happy with that terminology.  For simplicity though, I'll use that
term in this message.

If MDE satisfies the qualities of a sustainable softifact generating process,
then following the bullet points backwards supports the argument that we can
produce softifacts sustainably using MDE.  This argument is just on the process
though; MDE doesn't really dictate what artifacts we want.  That is a separate
research question.

- overlap
plus duplication - required and desired, but still want to be productive.  To be
productive, want to say once and view as needed.  Suggests generation - maybe
put this elsewhere?

@@

Further information on the relevant definitions and context is given in the next
section.  Roadmap.  Research questions for softifacts and knowledge.  Research
questions for the process.

\section{Good Research Questions}

The criteria for a good research question are :

Focused on a single problem or issue
Researchable using primary and/or secondary sources
Feasible to answer within the timeframe and practical constraints
Specific enough to answer thoroughly
Complex enough to develop the answer over the space of a paper or thesis
Relevant to your field of study and/or society more broadly

\section {Context, Definitions and Assumptions} \label{Sec_Context}

@@

\subsection{Definitions}

@@

\subsection{Assumptions}

@@

\subsection{Current State of the Practice Research Questions} \label{Sec_ResearchQuestions}

@@

\subsection{Ideal Process}
